Towards Automated Merging of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-05-10 sattose/paper.tex
Sattose Paper: Now with more content

\begin{table}[H]
  \begin{center}
  \caption{CloneRefactor results for Java projects corpus \cite{githubCorpus2013}.} \label{table:general}
  \bigskip
\begin{tabular}{|l|l|}
\hline
Amount of projects                                                                                      & 1,361      \\ \hline
\begin{tabular}[c]{@{}l@{}}Amount of lines (excluding\\ whitespace, comments and newlines.)\end{tabular} & 1,414,996  \\ \hline
Amount of statements/declarations                                                                       & 1,212,189  \\ \hline
Amount of tokens (excluding whitespace, comments and newlines.)                                                   & 11,643,194 \\ \hline
\end{tabular}
\end{center}
\end{table}

\subsection{Clone detection results}
Currently, we have implemented two clone detection algorithms into CloneRefactor. The first one finds clones by comparing tokens (excluding whitespace, comments and newlines). The second algorithm implements our type 1R, as explained in section \ref{chap:type1clones}.

\begin{table}[H]
  \begin{center}
  \caption{CloneRefactor results for Java projects corpus \cite{githubCorpus2013}.} \label{table:general}
  \bigskip
\begin{tabular}{|l|l|}
\hline
 & \textbf{Token} & \textbf{Type 1R}
\begin{tabular}[c]{@{}l@{}}Amount of lines cloned (excluding\\ whitespace, comments and newlines.)\end{tabular} & 200,362 & 129,519 \\ \hline
Amount of statements/declarations cloned & 182,466 & 118,980 \\ \hline
Amount of tokens cloned (excluding whitespace, comments and newlines.) & 1,582,845 & 973,596 \\ \hline
\end{tabular}
\end{center}
\end{table}

@@

\begin{table}[H]
  \begin{center}
  \caption{Clone relations} \label{table:relations}
  \bigskip
\begin{tabular}{|l|l|l|} \hline
\textbf{Relation}  & \textbf{Amount} & \textbf{Percentage} \\ \hline
Unrelated          & 13,529           & 39.37               \\ \hline
Same Class          & 8,341            & 24.28               \\ \hline
Sibling            & 5,978            & 17.40               \\ \hline
Same Method         & 2,456            & 7.15                \\ \hline
External Superclass & 2,402            & 6.99                \\ \hline
First Cousin        & 695             & 2.02                \\ \hline
Superclass         & 489             & 1.42                \\ \hline
Common Hierarchy    & 442             & 1.29                \\ \hline
Ancestor           & 28              & 0.08               \\ \hline
\end{tabular}
\end{center}
\end{table}

The most notable difference when comparing it to the results of Fontana et al. \cite{fontana2015duplicated} is that in our results 39.37\% of clone are unrelated, while for them it was only 15.70\%. This might be due to the fact that we consider clone classes rather than clone pairs, and mark the clone class ``Unrelated'' even if just one of the clone instances is outside a hierarchy. It could also be that the corpus which we use, as it has generally smaller projects, uses more classes from outside the project (which are marked ``Unrelated'' if they do not have a common external superclass). About a fourth of all clone classes have all instances in the same class, which is generally easy to refactor. On the third place come the ``Sibling'' clones, which can often be refactored using a pull-up refactoring.

@@

\begin{table}[H]
  \begin{center}
  \caption{Clone instance locations} \label{table:locations}
  \bigskip
\begin{tabular}{|l|l|l|}
\hline
\textbf{Location}  & \textbf{Amount}  & \textbf{Percentage} \\ \hline
Method Level       & 19,818           & 57.68               \\ \hline
Class Level        & 13,259           & 38.59               \\ \hline
Constructor Level  & 1,099            & 3.20                \\ \hline
Interface Level    & 110              & 0.32                \\ \hline
Enum Level         & 74               & 0.22                \\ \hline
\end{tabular}
\end{center}
\end{table}

Our results indicate that around 58\% of the clones are produced at method-level. About 39\% of clones either span several methods/constructors or contain something like a field declaration. Another 3\% of the clones are found in constructors. The amount of clones found in interfaces and enumerations is very low.

>>>>

\begin{table}[H]
  \begin{center}
  \caption{CloneRefactor results for Java projects corpus \cite{githubCorpus2013}.} \label{table:general}
  \bigskip
\begin{tabular}{|l|l|}
\hline
Amount of projects                                                                                      & 1,361      \\ \hline
\begin{tabular}[c]{@{}l@{}}Amount of lines (excluding\\whitespace, comments and newlines.)\end{tabular} & 1,414,996  \\ \hline
Amount of statements/declarations                                                                       & 1,212,189  \\ \hline
\begin{tabular}[c]{@{}l@{}}Amount of tokens (excluding\\whitespace, comments and newlines.)\end{tabular} & 11,643,194 \\ \hline
\end{tabular}
\end{center}
\end{table}

\subsection{Clone detection results}
Currently, we have implemented two clone detection algorithms into CloneRefactor. The first one finds clones by comparing tokens (excluding whitespace, comments and newlines), equal to the definition of type 1 clones in literature \cite{roy2007survey}. The second algorithm implements our type 1R, as explained in section \ref{chap:type1clones}. The differences between the clones found for these algorithms is displayed in table \ref{table:clonedet}. Please note that the amount of lines, statements and tokens is without whitespace, newlines and comments.

\begin{table}[H]
  \begin{center}
  \caption{CloneRefactor clone detection results for the two different algorithms.} \label{table:clonedet}
  \bigskip
\begin{tabular}{|l|l|l|}
\hline
Extra & \textbf{Type 1} & \textbf{Type 1R} \\ \hline
\begin{tabular}[c]{@{}l@{}}Amount of lines cloned\end{tabular} & 200,362 & 129,519 \\ \hline
\begin{tabular}[c]{@{}l@{}}Amount of statements/\\declarations cloned\end{tabular} & 182,466 & 118,980 \\ \hline
\begin{tabular}[c]{@{}l@{}}Amount of tokens cloned\end{tabular} & 1,582,845 & 973,596 \\ \hline
\end{tabular}
\end{center}
\end{table}

Looking at table \ref{table:clonedet}, it becomes apparent that the type 1R algorithm finds significantly less clones found than the type 1 algorithm. Figure \ref{fig:type1rclone} displays an example of a clone that does get detected by the type 1 algorithm but does not get detected by the type 1R algorithm. This is because the variable ``key'' and ``prefix'' are of a different primitive type between the clone instances. This makes this clone less suitable for automated refactoring. We manually checked some differences between the detected type 1 clones and type 1R clones and in each instance there was either a variable with different type, a different method call or a different type (but textual equality). This indicates that about a third of the clones have textual equality, but are not actually equal when considering the types of expressions.

\begin{figure}[H]
    \includegraphics[width=1\columnwidth]{img/clone}
  \caption{Example of a clone that is not a type 1R clone but is a type 1 clone.}
  \label{fig:type1rclone}
\end{figure}

@@

\begin{table}[H]
  \begin{center}
  \caption{Clone relations} \label{table:relations}
  \bigskip
\begin{tabular}{|l|l|l|l|l|} \hline
\textbf{Relation}  & \textbf{\# (1)} & \textbf{\% (1)}  & \textbf{\# (1R)} & \textbf{\% (1R)} \\ \hline
Unrelated          & 6,134           & 35.48  & 4,762 & 38.14            \\ \hline
\begin{tabular}[c]{@{}l@{}}Same\\Class\end{tabular}          & 4,772            & 27.60  & 3,131 & 25.07             \\ \hline
Sibling            & 2,680            & 15.50   & 1,949 & 15.61            \\ \hline
\begin{tabular}[c]{@{}l@{}}Same\\Method\end{tabular}         & 2,247            & 13.00   & 1,685 & 13.49             \\ \hline
\begin{tabular}[c]{@{}l@{}}External\\Superclass\end{tabular} & 794            & 4.59   & 558 & 4.47             \\ \hline
\begin{tabular}[c]{@{}l@{}}First\\Cousin\end{tabular}        & 269             & 1.56     & 197 & 1.58           \\ \hline
Superclass         & 237             & 1.37     & 118 & 0.94           \\ \hline
\begin{tabular}[c]{@{}l@{}}Common\\Hierarchy\end{tabular}    & 123             & 0.71    & 73 & 0.58            \\ \hline
Ancestor           & 35              & 0.20     & 14 & 0.11          \\ \hline
\end{tabular}
\end{center}
\end{table}

The most notable difference when comparing it to the results of Fontana et al. \cite{fontana2015duplicated} is that in our results most of the clones are unrelated (38.14\% with type 1R), while for them it was only 15.70\%. This might be due to the fact that we consider clone classes rather than clone pairs, and mark the clone class ``Unrelated'' even if just one of the clone instances is outside a hierarchy. It could also be that the corpus which we use, as it has generally smaller projects, uses more classes from outside the project (which are marked ``Unrelated'' if they do not have a common external superclass). About a fourth of all clone classes have all instances in the same class, which is generally easy to refactor. On the third place come the ``Sibling'' clones, which can often be refactored using a pull-up refactoring. There are no noteworthy differences between type 1 and type 1R clones.

@@

Please note that these results are measured over each clone instance rather than each clone class, hence the higher total amount in comparison to the results of section \ref{chap:ourmeasurements}.

\begin{table}[H]
  \begin{center}
  \caption{Clone instance locations} \label{table:locations}
  \bigskip
\begin{tabular}{|l|l|l|l|l|}
\hline
\textbf{Location}  & \textbf{\# T1} & \textbf{\% T1}  & \textbf{\# 1R} & \textbf{\% 1R} \\ \hline
Method Level       & 32,861           & 66.02   & 19,075 & 58.23            \\ \hline
Class Level        & 15,069           & 30.27   & 12,207 & 37.27            \\ \hline
\begin{tabular}[c]{@{}l@{}}Constructor\\Level\end{tabular}  & 1,391            & 2.79     & 1,080 & 3.30           \\ \hline
\begin{tabular}[c]{@{}l@{}}Interface\\Level\end{tabular}    & 282              & 0.57     & 247 & 0.75           \\ \hline
Enum Level         & 171               & 0.34    & 147 & 0.45            \\ \hline
\end{tabular}
\end{center}
\end{table}

Our results indicate that around 58\% of the clones are produced at method-level. About 39\% of clones either span several methods/constructors or contain something like a field declaration. Another 3\% of the clones are found in constructors. The amount of clones found in interfaces and enumerations is very low. Regarding the differences between type 1 and type 1R, it seems that there are relatively less method level clones and more class level clones for type 1R. This is probably due to that the main reason for variability between type 1 and type 1R is variable references, which occur more at method level than class level.
